Weighing Chances and Use Against Risks and Misuse of Emerging Genome Analysis and Manipulation Technology

### 2022-05-30 draft.tex
integrate Jennifers part

\author{\IEEEauthorblockN{1\textsuperscript{st} Benedict Bileam Scheuvens}
\IEEEauthorblockA{\textit{Data Science} \\
\textit{Hochschule Karlsruhe für Technik und Wirtschaft}\\
Karlsruhe, Germany \\
scbe1047@h-ka.de}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Jennifer Hilgenberg}
\IEEEauthorblockA{\textit{Data Science} \\
\textit{Hochschule Karlsruhe für Technik und Wirtschaft}\\
Karlsruhe, Germany \\
hije1012@h-ka.de}
}

@@

\begin{abstract}
A few centuries ago, life love and a the universe were a mystery, but driven by deeply rooted human curiosity we are beginning to untangle the mess and understand the foundation that grew consciousness out of thin air. One piece of this puzzle is the molecule of life, DeoxyriboNucleic Acid. The genetic material that after being refined by millenia of pure chance and survival holds the blueprint to every living creature on our planet. With growing understanding about its structure and the technological advancements that gave us tools to manipulate it, humanity has set its foot in the doorstep to a world in which DNA is no different than a LEGO brick and nothing is out of reach.
This paper aims to explore aspects of how applied genetics will impact us in regard to ethics and data privacy. 
Since great responsibility comes with great power, Genetic engineering is as much blessing as curse and must be used with caution, while genome analysis unveils a tremendous amount of information not just about us, but about our relatives as well and enables more and more accurate predictions about the future.
\end{abstract}
\section{Historical and Technical Introduction}

>>>>

\author{\IEEEauthorblockN{1\textsuperscript{st} Benedict Bileam Scheuvens}
\IEEEauthorblockA{\textit{Data Science} \\
\textit{Hochschule Karlsruhe}\\
\textit{University of Applied Sciences} \\
scbe1047@h-ka.de}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Jenny Hilgenberg}
\IEEEauthorblockA{\textit{Data Science} \\
\textit{Hochschule Karlsruhe}\\
\textit{University of Applied Sciences} \\
Karlsruhe, Germany \\
hije1011@h-ka.de}
}

@@

\begin{abstract}
A few centuries ago, life love and a the universe were a mystery, but driven by deeply rooted human curiosity we are beginning to untangle the mess and understand the foundation that grew consciousness out of thin air. One piece of this puzzle is the molecule of life, DeoxyriboNucleic Acid. The genetic material that after being refined by millenia of pure chance and survival holds the blueprint to every living creature on our planet. With growing understanding about its structure and the technological advancements that gave us tools to manipulate it, humanity has set its foot in the doorstep to a world in which DNA is no different than a LEGO brick and nothing is out of reach.
This paper aims to explore aspects of how applied genetics will impact us in regard to ethics and data privacy. 
Since great responsibility comes with great power, Genetic engineering is as much blessing as curse and must be used with caution, while genome analysis unveils a tremendous amount of information not just about us, but about our relatives as well and enables more and more accurate predictions about the future.
This paper summarises the chances and risks of genome analysis broken down in three fundamental questions. \textit{Who are you} focuses on the individual consumer of DNA tests, what is expected to gain from the results and why it is growing in popularity. \textit{What have you done} takes a look at the past of an individual and what information can be tracked by DNA. \textit{What does your future look like} aims at the consequences this information can have.
\end{abstract}
\section{Historical and Technical Introduction}
